E1-analysis-comparison-to-JMW23

### 2024-06-07 group-a/E1-analysis-comparison-to-Hartshorne.Rmd
edits to manuscript and exp 1

#check for weirdness
discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
  (audio.data$duration_of_verb + 
     audio.data$duration_of_intervening_determiner + 
     audio.data$intonation_break_bw_verb_and_determiner)
sum(discrep) 
#this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
```

@@

#### Cumulative Fixation Probabilities
For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-JH-spaghetti-fig).

```{r E1-JH-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total))

jh_E1_spag_fig

#The "Object type" part of the key doesn't actually show which color is which
```

@@

jh.E1_model1_tab.min = broom.mixed::tidy(jh.E1_model1.min) 
jh.E1_model1_obj.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model1_verb.min = jh.E1_model1_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model1_obj_verb.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations 
<!--AJ: Edit text -->
In our first two analyses, we ask whether participants looked more to the target than to the distractor during the predictive time window, given that the verb is restricting. The first model tested whether there were more fixations to the target object than to the distractor in the time window before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and images (with no covariance between random effects because the model cannot converge with full covariance matrix). There were no significant effects, although the critical interaction was in the right direction [bar graph?] (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model2_tab.min = broom.mixed::tidy(jh.E1_model2.min) 
jh.E1_model2_obj.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model2_verb.min = jh.E1_model2_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model2_obj_verb.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we do the same, we again see that the critical interaction is not significant but numerically in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model3_tab.min = broom.mixed::tidy(jh.E1_model3.min) 
jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")

```
#### First target fixations after verb
Finally, we address whether participants look to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. [TO-DO: On average, participants looked to the target X ms after (AK's Table 1)..., I'll also want to say the lengths of the verbs. AK's Table 2] We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; participants looked sooner at the target in the restrictive condition, while accounting for verb duration and its interaction with condition, but this was not a statistically significant effect (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

We tested whether a participant's calibration quality was correlated with their effect size. Across the three condition effects of interest, calibration quality was not significantly correlated (Effect 1 (pre-noun-onset): Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`, Effect 2 (pre-verb-offset): Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`, Effect 3 (first fixation): Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).

>>>>

# #check for weirdness
# discrep <- audio.data$delay_bw_onset_of_verb_and_onset_of_target_noun - 
#   (audio.data$duration_of_verb + 
#      audio.data$duration_of_intervening_determiner + 
#      audio.data$intonation_break_bw_verb_and_determiner)
# sum(discrep) 
# #this should be zero, but it's 0.59! TO-DO: Check out the 3rd (audio/2r.mp3) and 22nd item (audio/11nr.mp3)
```

@@

#### Cumulative Fixation Probabilities
For each sentence, the target time window began at the onset of the verb and ended 2000 milliseconds later. This window was then divided into 50-ms bins; for each participant and each trial, we recorded whether each object was fixated during the 50-ms bin. Collapsing over trials and participants, and averaging across distractors, we calculated the cumulative probability of fixation, shown in Figure  \@ref(fig:E1-spaghetti-fig), Panel (c).

```{r make jh spaghetti plot}

jh_E1_spag_fig <- ggplot(jh.cumulative.fixation.data.summary.min, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  geom_line()+
  geom_point(aes(fill = object_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c(distractor = "white", target.object = "black"), labels = c("distractor", "target"))+
  scale_shape_manual(values=c(22,21))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")+
  geom_vline(xintercept = mean(jh.word.dur.avg$Total)) +
  theme(panel.grid=element_blank(), legend.position = "none")+
  ggtitle('In-lab sample')

#jh_E1_spag_fig

@@

jh.E1_model1_tab.min = broom.mixed::tidy(jh.E1_model1.min) 
jh.E1_model1_obj.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model1_verb.min = jh.E1_model1_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model1_obj_verb.min = jh.E1_model1_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-noun fixations 
In line with the previous analyses of the remote data, we asked whether participants looked more to the target than to the distractor object during the predictive time window, depending upon the verb condition. The first model constrained the predictive window to the time before the onset of the target noun. We ran a regression model predicting the cumulative fixation probability in the last 50-ms bin before noun onset from the verb condition (restricting = 1 vs. non-restricting = 0), object type (target = 1 vs. distractor = 0), and their interaction, along with random effects for participants and scenes (with no covariance between random effects because the model cannot converge with full covariance matrix). Unlike the remote sample, there was a significant main effect of object type such that participants were more likely to be looking at the target than the distracter object during this time window (_b_ = `r jh.E1_model1_obj.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj.min %>% pull(p.value) %>% round(digits = 2)`). Also unlike the remote sample, the critical interaction was not in the expected direction, although it was also not statistically significant (_b_ = `r jh.E1_model1_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model1_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model1_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model2_tab.min = broom.mixed::tidy(jh.E1_model2.min) 
jh.E1_model2_obj.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object")
jh.E1_model2_verb.min = jh.E1_model2_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model2_obj_verb.min = jh.E1_model2_tab.min %>% filter(term == "object_classtarget.object:verb_typerestricting")
```
#### Pre-verb-offset fixations
Altmann & Kamide tested a second model, aligning the predictive time window with the offset of the verb rather than the onset of the noun as above. When we did the same, we again saw that the critical interaction is not significant nor in the expected direction (_b_ = `r jh.E1_model2_obj_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model2_obj_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model2_obj_verb.min %>% pull(p.value) %>% round(digits = 2)`).

@@

jh.E1_model3_tab.min = broom.mixed::tidy(jh.E1_model3.min) 
jh.E1_model3_verb.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting")
jh.E1_model3_dur.min = jh.E1_model3_tab.min %>% filter(term == "dur_verb_ms_c")
jh.E1_model3_intxn.min = jh.E1_model3_tab.min %>% filter(term == "verb_typerestricting:dur_verb_ms_c")
```
#### First target fixations after verb
Finally, we addressed whether participants looked to the target faster in the restrictive vs. the non-restrictive condition, starting after the onset of the verb. On average, participants looked to the target `r jh.our_table1_min$Eat[4]` ms after the noun onset in the restrictive condition and `r jh.our_table1_min$Move[4]` ms after the noun onset in the non-restrictive condition. As in the remote sample, the latencies are overall slower than in results published by Altmann & Kamide (1999) and James et al. (2023). Unlike in the remote sample, however, the difference is in the unexpected direction, such that participants looked to the target faster in the non-restrictive condition.

We ran a regression model predicting the timing of the first fixation to the target object, relative to the onset of the noun, with verb condition as a predictor, mean-centered verb duration as a covariate, and random intercepts and condition slopes for participants and scenes. There were no significant effects; results revealed that the paradoxical advantage in the non-restrictive condition was not statistically significant (_b_ = `r jh.E1_model3_verb.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_verb.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_verb.min %>% pull(p.value) %>% round(digits = 2)`). Effects of verb duration and its interaction with condition were also not statistically significant (duration: _b_ = `r jh.E1_model3_dur.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_dur.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_dur.min %>% pull(p.value) %>% round(digits = 2)`; interaction: _b_ = `r jh.E1_model3_intxn.min %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r jh.E1_model3_intxn.min %>% pull(std.error) %>% round(digits = 2)`, _p_=`r jh.E1_model3_intxn.min %>% pull(p.value) %>% round(digits = 2)` )

@@

We tested whether a participant's calibration quality was correlated with their effect size. Across the three condition effects of interest, calibration quality was not significantly correlated (pre-noun: Pearson's _r_ = `r jh.m1_diffdiff_cor_r`, _p_ = `r jh.m1_diffdiff_cor_p`; pre-verb-offset: Pearson's _r_ = `r jh.m2_diffdiff_cor_r`, _p_ = `r jh.m2_diffdiff_cor_p`; first fixation: Pearson's _r_ = `r jh.m3_diff_cor_r`, _p_ = `r jh.m3_diff_cor_p`. However, when the two interaction effects are calculated as the target advantage in the restricting condition only (i.e. rather than a difference of differences), we see a significant correlation between target advantage and calibration quality in the wider pre-noun window (Pearson's _r_ = `r jh.m1_diff_cor_r`, _p_ = `r jh.m1_diff_cor_p`).

<!--###AGGRESSIVE EXCLUSION-->
<!-- Set which mode here: -->
```{r}
# 'AGGRESSIVE' or 'MINIMAL'
exclusion.mode <- 'AGGRESSIVE' 
```

```{r}
prop.samples.threshold.aggro.jh <- 0.2

bad.subjects.prop.samples.aggro.jh <- jh.prop.in.roi.by.subject %>%
  filter(prop.of.samples.in.roi <= prop.samples.threshold.aggro.jh) %>%
  pull(subject_id)
```

<!-- Set criteria for minimal and aggressive exclusions -->

```{r}
validation.threshold.aggro.jh <- 50

bad.subjects.validation.aggro.jh <- jh.validation.percent %>%
  filter(M <= validation.threshold.aggro.jh) %>%
  pull(subject_id) %>%
  as.character()
```

```{r}
bad.subjects.aggro.jh <- unique(c(bad.subjects.prop.samples.aggro.jh, bad.subjects.validation.aggro.jh))

critical.trials.filtered.aggro.jh <- jh.critical.trials %>%
  filter(!subject_id %in% bad.subjects.aggro.jh)

n.bad.subjects.aggro.jh <- length(bad.subjects.aggro.jh)
```
#### Aggressive Exclusion
The second set of analyses used more aggressive exclusion criteria. First, we eliminated participants with `r prop.samples.threshold.aggro.jh*100` percent of fixations or fewer landing in any ROIs. This resulted in the elimination of `r length(bad.subjects.prop.samples.aggro.jh)` participants. Second, we excluded participants with validation accuracy under `r validation.threshold.aggro.jh` percent, which eliminated an additional `r n.bad.subjects.aggro.jh - length(bad.subjects.prop.samples.aggro.jh)` participants. The following analyses included `r nlevels(droplevels(critical.trials.filtered.aggro.jh$subject_id))` participants.

```{r}
cumulative.fixation.data.aggro.jh <- critical.trials.filtered.aggro.jh %>%
  mutate(t.relative.to.verb.onset = t - (verb_onset*1000)) %>%
  filter(t.relative.to.verb.onset >= 0 & t.relative.to.verb.onset <2000) %>%
  mutate(t.w = floor(t.relative.to.verb.onset/50)*50)
```

```{r}

if(file.exists("data/generated/cumulative_fixation_data_aggro.jh.csv")){
  cumulative.fixation.windows.data.aggro.jh <- read_csv("data/generated/cumulative_fixation_data_aggro.jh.csv")
} else {

  cumulative.fixation.windows.data.aggro.jh <- cumulative.fixation.data.aggro.jh %>%
    group_by(subject_id, verb_type, image_name, object_type, object_class) %>%
    summarize(cumulative.fixation.calculation(cur_data()))

  write_csv(cumulative.fixation.windows.data.aggro.jh, file ="data/generated/cumulative_fixation_data_aggro.jh.csv")
}
```

```{r}
cumulative.fixation.windows.grouped.data.aggro.jh <- cumulative.fixation.windows.data.aggro.jh %>%
  filter(!subject_id %in% bad.subjects.aggro.jh) %>%
  group_by(subject_id, verb_type, image_name, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(has.fixated)) 
```

```{r}
cumulative.fixation.windows.grouped.average.data.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
  group_by(subject_id, verb_type, object_class, t.window) %>%
  summarize(cumulative.fixation.p = mean(cumulative.fixation.p))
```

```{r}
cumulative.fixation.data.summary.aggro.jh <- cumulative.fixation.windows.grouped.average.data.aggro.jh %>%
  filter(object_class %in% c('target.object', 'distractor')) %>%
  group_by(t.window, verb_type, object_class) %>%
  summarize(cumulative.fixation.m = mean(cumulative.fixation.p))
```

```{r} 
#|E1-spaghetti-fig, 
#|fig.cap = "Cumulative probability of fixating distractor 
#|,and target objects across conditions."
E1_spag_fig_aggro.jh <- ggplot(cumulative.fixation.data.summary.aggro.jh, aes(x=t.window, y=cumulative.fixation.m, fill=object_class, shape=verb_type, group=interaction(verb_type, object_class)))+
  scale_fill_grey(start=1.0, end=0.0)+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type")

#TO-DO: insert a vertical line for the average noun onset
```

```{r}
noun.onset.times.aggro.jh <- critical.trials.filtered.aggro.jh %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, delay_bw_onset_of_verb_and_onset_of_target_noun) %>%
  mutate(relative.noun.onset = delay_bw_onset_of_verb_and_onset_of_target_noun * 1000) %>%
  select(-delay_bw_onset_of_verb_and_onset_of_target_noun)

trial.level.cumulative.fixation.data.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
  left_join(noun.onset.times.aggro.jh, by=c("image_name", "verb_type"))
```

```{r}
pre.noun.first.looks.data.aggro.jh <- trial.level.cumulative.fixation.data.aggro.jh %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.noun.onset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r}
pre.noun.first.looks.data.aggro.jh$verb_type <- as.factor(pre.noun.first.looks.data.aggro.jh$verb_type)
pre.noun.first.looks.data.aggro.jh$object_class <- as.factor(pre.noun.first.looks.data.aggro.jh$object_class)
```
<!--Fit the model, with no covariance between random effects because the model cannot converge with full covariance matrix.-->

```{r}
E1_model1.aggro.jh <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.noun.first.looks.data.aggro.jh)
#summary(E1_model1.aggro.jh)

E1_model1_tab.aggro.jh = broom.mixed::tidy(E1_model1.aggro.jh) 
E1_model1_obj.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "object_classtarget.object")
E1_model1_verb.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "verb_typerestricting")
E1_model1_obj_verb.aggro.jh = E1_model1_tab.aggro.jh %>% filter(term == "object_classtarget.object:verb_typerestricting")
```

```{r}
verb.offset.times.aggro.jh <- critical.trials.filtered.aggro.jh %>%
  group_by(image_name, verb_type) %>%
  slice(1) %>%
  ungroup() %>%
  select(image_name, verb_type, duration_of_verb) %>%
  mutate(relative.verb.offset = duration_of_verb * 1000) %>%
  select(-duration_of_verb)

trial.level.cumulative.fixation.data.verb.offset.aggro.jh <- cumulative.fixation.windows.grouped.data.aggro.jh %>%
  left_join(verb.offset.times.aggro.jh, by=c("image_name", "verb_type"))
```

```{r}
pre.verb.offset.first.looks.data.aggro.jh <- trial.level.cumulative.fixation.data.verb.offset.aggro.jh %>%
  group_by(subject_id, image_name, verb_type) %>%
  filter(t.window < relative.verb.offset) %>%
  filter(t.window == max(t.window)) %>%
  filter(object_class %in% c("target.object", "distractor"))
```

```{r}

E1_model2.aggro.jh <- afex::lmer_alt(cumulative.fixation.p ~ object_class * verb_type + (object_class * verb_type || image_name) + (object_class * verb_type || subject_id) , data=pre.verb.offset.first.looks.data.aggro.jh)
#summary(E1_model2.aggro.jh)

E1_model2_tab.aggro.jh = broom.mixed::tidy(E1_model2.aggro.jh) 
E1_model2_obj.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "object_classtarget.object")
E1_model2_verb.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "verb_typerestricting")
E1_model2_obj_verb.aggro.jh = E1_model2_tab.aggro.jh %>% filter(term == "object_classtarget.object:verb_typerestricting")
```

```{r}
first.fixation.after.verb.onset.aggro.jh <- critical.trials.filtered.aggro.jh %>%
  group_by(subject_id, image_name) %>%
  filter(t >= verb_onset*1000) %>%
  filter(object_type == "target.object") %>%
  filter(is.fixating == TRUE) %>%
  filter(t == min(t)) %>%
  mutate(noun_relative.t = t - (postverbal_noun_onset*1000)) %>%
  mutate(von_relative.t = t - (verb_onset*1000)) %>%
  mutate(voff_relative.t = t - (verb_offset*1000)) %>%
  mutate(det_relative.t = t -(postverbal_determiner_onset*1000))
```

```{r}
first.fixation.after.verb.onset.analysis.data.aggro.jh <- first.fixation.after.verb.onset.aggro.jh %>%
  ungroup() %>%
  select(subject_id, image_name, verb_type, duration_of_verb, noun_relative.t) %>%
  mutate(dur_verb_ms_c = scale(duration_of_verb, scale = FALSE)*1000) #mean-center verb duration
```

```{r}
E1_model3.aggro.jh <- lmer_alt(noun_relative.t ~ verb_type*dur_verb_ms_c + (verb_type || subject_id) + (verb_type || image_name), data=first.fixation.after.verb.onset.analysis.data.aggro.jh)

#summary(E1_model3.aggro.jh)

E1_model3_tab.aggro.jh = broom.mixed::tidy(E1_model3.aggro.jh) 
E1_model3_verb.aggro.jh = E1_model3_tab.aggro.jh %>% filter(term == "verb_typerestricting")

```
Across all three models, results were in line with analyses using the minimal exclusion criteria; none of the critical effects were statistically significant, nor were they in the expected direction (Pre-noun-onset window, verb x object interaction: _b_ = `r E1_model1_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model1_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model1_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Pre-verb-offset window, verb x object interaction: _b_ = `r E1_model2_obj_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model2_obj_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model2_obj_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`; Verb effect on first target fixation: _b_ = `r E1_model3_verb.aggro.jh %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E1_model3_verb.aggro.jh %>% pull(std.error) %>% round(digits = 2)`, _p_=`r E1_model3_verb.aggro.jh %>% pull(p.value) %>% round(digits = 2)`).

### 2024-06-07 group-a/E1-analysis-comparison-to-JMW23.Rmd
edits to manuscript and exp 1

```{r setup, include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)

@@

```{r import JMW23}
JMW1_info <- read_csv("group-a/JMW23-data/fyptrialinfo.csv")

JMW1_latency <- read.delim("group-a/JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = FALSE, sep = ",") #I'll come back to this

JMW1_data <- read.delim("group-a/JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")

@@

#Now use it to summarize timecourse data
if(file.exists("group-a/JMW23-data/generated/JMW_cumulative.csv")){
  JMW_cumu<- read_csv("group-a/JMW23-data/generated/JMW_cumulative.csv")
} else {

@@

  write_csv(JMW_cumu, file="group-a/JMW23-data/generated/JMW_cumulative.csv")
}
```

@@

```{r group cumu fix by object, message=FALSE, warning=FALSE}
JMW_cumu.windows.grouped <- JMW_cumu %>%
  group_by(SUBJ, COND, AID, obj_class, t.window) %>%
  summarize(cumu.p = mean(has.fixated)) 
```

@@

```{r collapse cumu fix over trials, message=FALSE, warning=FALSE}
JMW_cumu.windows.grouped.average <- JMW_cumu.windows.grouped %>%
  group_by(SUBJ, COND, obj_class, t.window) %>%
  summarize(cumu.p.avg = mean(cumu.p))
```

@@

```{r create summary data for spag plot, message=FALSE, warning=FALSE}
JMW_cumu.summary <- JMW_cumu.windows.grouped.average %>%
  filter(obj_class %in% c('TARGET', 'DISTRACTOR')) %>%
  group_by(t.window, COND, obj_class) %>%
  summarize(cumulative.fixation.m = mean(cumu.p.avg))
```
```{r JMW-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

#AJ: this is where you left off. Everything above should work :)
JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND, group=interaction(COND, obj_class)))+
  scale_fill_manual(values=c("white", "black"))+
  scale_shape_manual(values=c(22,21))+
  geom_line()+
  geom_point(size=2)+
  theme_bw()+
  theme(panel.grid=element_blank())+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative))
#The "Object type" part of the key doesn't actually show which color is which
```

>>>>

```{r setup JMW23, include=FALSE}
library(papaja)
library(jsonlite)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(stringr)
library(lmerTest)
library(afex)
library(forcats)
library(broom.mixed)

@@

```{r import JMW23}
JMW1_info <- read_csv("JMW23-data/fyptrialinfo.csv")

JMW1_latency <- read.delim("JMW23-data/FYPAKFixationLatenciesPOSTVERB.txt", header = TRUE) #it's actual onset times (relative to trial start).

JMW1_data <- read.delim("JMW23-data/FYPTimecourse_by_subj.txt", header = FALSE, sep = ",")

@@

#Now use it to summarize timecourse data
if(file.exists("JMW23-data/generated/JMW_cumulative.csv")){
  JMW_cumu<- read_csv("JMW23-data/generated/JMW_cumulative.csv")
} else {

@@

  write_csv(JMW_cumu, file="JMW23-data/generated/JMW_cumulative.csv")
}
```

@@

```{r group cumu fix by object jmw, message=FALSE, warning=FALSE}
JMW_cumu.windows.grouped <- JMW_cumu %>%
  group_by(SUBJ, COND, AID, obj_class, t.window) %>%
  summarize(cumu.p = mean(has.fixated)) 
```

@@

```{r collapse cumu fix over trials jmw, message=FALSE, warning=FALSE}
JMW_cumu.windows.grouped.average <- JMW_cumu.windows.grouped %>%
  group_by(SUBJ, COND, obj_class, t.window) %>%
  summarize(cumu.p.avg = mean(cumu.p))
```

@@

```{r create summary data for spag plot jmw, message=FALSE, warning=FALSE}
JMW_cumu.summary <- JMW_cumu.windows.grouped.average %>%
  filter(obj_class %in% c('TARGET', 'DISTRACTOR')) %>%
  group_by(t.window, COND, obj_class) %>%
  summarize(cumulative.fixation.m = mean(cumu.p.avg))
```

```{r JMW-spaghetti-fig, fig.cap = "Cumulative probability of fixating distractor and target objects across conditions over time, with 0 ms aligned to the verb onset time. The vertical line marks the mean noun onset time across trials and conditions."}

JMW_spag_fig <- ggplot(JMW_cumu.summary, aes(x=t.window, y=cumulative.fixation.m, fill=obj_class, shape=COND))+
  geom_line()+
  geom_point(aes(fill = obj_class), size=2, color = "black")+ 
  scale_fill_manual(name = "Object Type",values=c("white", "black"), labels = c("distractor", "target"))+
  guides(fill = guide_legend(override.aes=list(shape=21))) +
  scale_shape_manual(name = "Verb Type", values=c(22,21), labels = c("non-resticting", "restricting"))+
  theme_bw()+
  scale_y_continuous(limits=c(0,1))+
  scale_x_continuous(expand=c(0.01,0.01))+
  labs(x="Time from Verb Onset (ms)", y="Probability", shape="Verb Type", fill="Object Type") +
  geom_vline(xintercept = mean(JMW1_info$Non.relative)) +
  theme(panel.grid=element_blank(), legend.position = "none", axis.title.x = element_blank())+
  ggtitle('James et al. (2023), Exp. 1')

#JMW_spag_fig
```

```{r JMW23 latency info}
#View(JMW1_latency)
JMW1_latency$COND <- recode(JMW1_latency$COND, "0" = "filler", "1" = "pred", "2" = "neut")

#Merge with data about word onset times to get relative onsets
JMW1_latency_info <- merge(JMW1_latency, JMW1_info, by.x = "ITEM", by.y = "AID") #in the second spreadsheet, TARGET etc mean the coordinates (now TARGET.y, AGENT.y, etc.). in the first, it means the first fixation time (now TARGET.x, etc.)

#Get relative target fixation times
JMW1_lat <- JMW1_latency_info %>%
  filter(TARGET.x >= Von) %>%
  mutate(von_relative_t = TARGET.x - Von,
         voff_relative_t = TARGET.x - Voff,
         non_relative_t = TARGET.x - Non)

#hist(JMW1_lat$von_relative_t)

first.fix.avg.JMW <- JMW1_lat %>%
  group_by(COND) %>%
  summarize(Verb.on = round.comm(mean(von_relative_t, na.rm = T)),
            Verb.off = round.comm(mean(voff_relative_t, na.rm = T)),
            Noun.on = round.comm(mean(non_relative_t, na.rm = T)))
```
